\section{Invited Talks at Conferences and Workshops}
\begin{enumerate}
\ifrecent{2019}{
\item Psi-k Total Energy and Forces conference, 9-11.01.2019, ICTP Trieste. Invited Talk - “Physics-Based Machine Learning for Atomistic Modeling”
\item Workshop on Theoretical Chemistry 2019, 26.02-01.03.2019, Mariapfarr. Three lectures on “Accelerated and Advanced path integral methods”
\item ACS National Meeting, 31.03-04.04.2019, Orlando. Invited Talk - “Physics-based machine learning for materials and molecules”
\item SCS Spring Meeting, 05.04.2019, EMPA Dübendorf. Keynote Talk - “Physics-Based Machine Learning for Atomistic Modelling”
}
\ifrecent{2018}{
\item Helsinki Winter School in Theoretical Chemistry, 10-13.12.2018, Helsinki. Two lectures on “Atom-density based representations for machine learning” and “Not only potentials: learning vectors and tensors”
\item Lorentz Center Workshop “Machine Learning and Reverse Engineering for Soft Materials”, 10-14.12.2018. Invited talk “Atomic structure representations between supervised and unsupervised learning”
\item CECAM Discussion Meeting “Coarse-graining with Machine Learning in molecular dynamics”, 5-17.12.2018, SANOFI Paris. Invited talk “Physics-Based Machine Learning for Materials and Molecules”
\item RCTF18, 08-12.10.2018, Toulouse, Keynote Talk: “Machine-learning like a physicist”
\item Sackler-CECAM Workshop on “Frontiers in Molecular Dynamics”, 10-12.10.2018, Tel Aviv. Invited Talk: “Physics-based Machine Learning”
\item ECAM State-of-the Art Workshop: “Large scale activated event simulations”, 1-3.10.2018, Vienna. Invited Talk: “ Machine-learning of materials between predictions and insights”
\item AI4MATER “Application of Machine Learning for Materials Science” 25.09.2018, ICMPE Paris. Invited Talk: “Machine-learning like a physicist”
\item NOMAD Summer 2018 “A hands-on course on tools for novel-materials discovery”, 24-27.09.2018, EPFL. Lecture on “Machine-learning of materials between predictions and insights”
\item CECAM School PI2018 “Path Integral Quantum Mechanics: From the Basics to the Latest Developments”, 25-29.06.2018, EPFL. Lecture on “Accelerated (and Advanced) Path Integral Methods”
\item Energy Landscapes 2018, 02-09.08.2018, Kalamata (Greece), Invited Talk: “Machine-learning like a physicist”
\item TSRC Meeting, 9-12.07.2018, Telluride (CO), Invited Talk “Modelling of second-harmonic scattering from aqueous solutions”
\item SIAM Conference on Mathematical Aspects of Materials Science, 8-13.07.2018, Portland (OR). Plenary Talk - “Symmetry Matters: Machine Learning of Scalar and Tensorial Atomic-Scale Properties”
\item EMMC Meeting, 11-13.06.2018, Upssala. Keynote Talk - “Machine learning like a physicist”
\item FHI Theory Symposium, 4-5.04.2018, Fritz-Haber Institute, Berlin. Invited Talk - “Machine learning for materials and molecules: energy, properties and insights”
\item DPG Spring Meeting, 12-17.03.2018, TU Berlin. Invited Talk - “A Generally-Applicable Machine-Learning Scheme for Materials and Molecules”
\item APS March Meeting, 4-10.03.2018, Los Angeles. Invited Talk - “Symmetry Matters: Machine-learning of Scalar \&{} Tensorial Atomic-Scale Properties”
\item CP2K Meeting, 8.02.2018, ENS Lyon. Invited Talk “Advanced Sampling and Quantum Effects with CP2K and i-PI”
\item Psi-k Total Energy and Forces conference, 9-11.01.2018, Cambridge. Invited Talk - “A Generally-Applicable Machine-Learning Scheme for Materials and Molecules”
}
\ifrecent{2017}{
\item NIPS 2017 Workshop “Machine Learning for Molecules and Materials”, Los Angeles 4-9.12.2017. Invited talk: “Symmetry Matters: Machine Learning of Tensorial Properties of Materials and Molecules.”
\item IPAM Workshop on “Uncertainty Quantification for Stochastic Systems and Applications”, Los Angeles, 13-17.11.2017. Invited talk “Learning and Correcting Static and Dynamic Properties of Materials in Atomistic Simulations”.
\item International Workshop in Electron-volt Neutron Spectroscopy, Rome, 7-8.11.2017. Invited talk “Theoretical benchmarks of deep inelastic neutron scattering. From the kinetic energy to the full particle momentum distribution”
\item CPMD 2017, Tsukuba, 18-20.10.2017. Invited talk “A Generally-Applicable Machine-Learning Scheme for Materials and Molecules”
\item Hands-on Workshop Density-Functional Theory and Beyond, Humboldt University, Berlin, 31.07-11.09.2017. Invited lecture on “Dimensionality reduction for Big-Data analytics”
\item TSRC Meeting on quantum effects, Telluride, 24-28.07.2017. Invited talk on “Solvent Fluctuations and Nuclear Quantum Effects Modulate the Molecular Hyperpolarizability of Water”
\item NSF/CECAM school on Computational Materials Science, EPFL, 1-17.07.2017. Invited lectures on “Advanced Molecular Dynamics: Thermostats, Barostats and Nuclear Quantum Effects” and “A generally applicable machine-learning scheme for materials and molecules”
\item PLUMED User Meeting 2017, SISSA Trieste, 25-27.05.2017. Invited talk on “Bridging the gap between atomistic and mesoscopic models of nucleation”
\item CECAM Workshop “Exploiting finite-size effects in simulations”, UPMC Paris, 18-21.4.2017. Invited talk on “Bridging the gap between atomistic and mesoscopic models of nucleation”
\item Finnish Physics Days, Helsinki, 21-24.03.2017. Invited talk on “Machine learning for materials and molecules”
\item MPG-EPFL Workshop, Ascona, 6-10.03.2017. Invited talk on “Machine learning for materials and molecules”
\item CCMX Winter School, 30.01-03.02.2017, Lecture on “Atomistic modelling of solidification in out-of-equilibrium conditions”
}
\ifrecent{2016}{
\item IPAM Workshop “Machine Learning Meets Many-Particle Problems”, IPAM/UCLA, Los Angeles 26-30/9/2016. Invited talk: “Using machine learning to map the structure and predict the properties of materials and molecules”
\item JCP Conference “Future of Chemical Physics”, 31.08-02.09.2016, Oxford. Invited talk “Using machine learning to map the structure and predict the properties of materials and molecules”
\item Workshop “Reaction Coordinates from Molecular Trajectories”, 29.08-2.09.2016, Leiden. Invited talk “Finding Patterns and Mapping Landscapes”
\item CCMX Summer School on Multiscale Modelling of Materials, 29-31/8/2016, Lausanne. Invited Lecture “Advanced Molecular Dynamics”
\item Workshop “Frontiers of Solidification”, 29-30.07.2016, Shanghai. Invited talk “Modelling nucleation at finite undercooling.”
\item Workshop “Interfacial Molecular and Electronic Structure and Dynamics”, 18-21.07.2016, Telluride (CO). Invited talk “Simulating Second Harmonic Scattering from Solutions”
\item CECAM/Psi-k School on Path Integral Quantum Mechanics: Theory, Simulation and Applications, 13-17/6/2016, Lausanne. Lecture “Accelerating Path Integrals ”
\item CECAM-ETHZ, 01/06/2016, Zürich. Invited Talk “Distances, maps and properties. Machine learning for materials and molecules”
\item SIAM Uncertainty Quantification, April 2016. Invited talk “Mapping the structural and alchemical landscape of materials, from molecules to the condensed phase”
\item SACC Spring Meeting, Bern, 05/02/2016. Invited talk “Distances and kernels for materials and molecules. From structure to properties”
\item CECAM Workshop on “Liquid/Solid Interfaces”, EPFL-CECAM, 25-27/01/2016. Invited talk “Nanoscale self-assembly of water and alcohol at the interface with graphite”
}
\ifrecent{2015}{
\item Workshop on “Predictive Multiscale Materials Modelling”, TGM Cambridge, 1-4/12/2015. Invited talk “From atomic environments to meso-scale structures. Mapping complexity in materials”
\item Workshop on “Recent Advances in Machine Learning and Applications”, Nagoya (Japan) 5-6/11/2015. Invited talk “Finding Patterns and Drawing Maps of the Complex Structural Landscapes of Materials and Molecules”
\item CCCS Symposium “Machine learning in science”, Basel 3/11/2015. Invited talk “Unraveling Structural Complexity with Machine Learning”
\item CECAM-ESI Workshop "From trajectories to reaction coordinates: making sense of molecular simulation data", Vienna 16-18/9/2015. Invited talk “Automatic recognition of molecular patterns in atomistic simulations”
\item ICTP School on Computational Condensed Matter Physics, Trieste 7-25/9/2015. Two invited lectures on “Modeling the Quantum Nature of Atomic Nuclei by Imaginary Time Path Integrals” and “Representing and understanding patterns in materials and molecules”
\item MPG-EPFL Summer School, Ringberg, 27-31/7/2015. Invited talk: “Representing and Understanding patterns in Materials and Molecules.”
\item TSRC Meeting, Telluride, USA, 20-24/7/2015. Invited talk: “Colored Noise for PIMD: State of the Art and Latest Developments”
\item CECAM Meeting “Molecular Quantum Dynamics Methods: Benchmarks and State of the Art”, EPFL, 15-19/6/2015. Invited talk: “Path integrals, *MD (and Colored Noise)”
\item PASC 2015, Zürich, 1-3/6/2015. Invited talk: “Machine-learning molecular patterns in atomistic simulations”
\item Mod-PMI Workshop, Marseille, France, 25-27/5/2015. Invited talk: “Quantum nuclei in materials: (when) do we need to worry?”
\item Symposium on “Big Data and Predictive Computational Modeling”, IAS-TUM Münich, Germany, 18-21/5/2015. Keynote talk: “Finding Patterns and Drawing Maps in the Configuration Space of Materials and Molecules”
\item Juelich Winter School “Computational Trends in Solvation and Transport in Liquids” Jülich, Germany, 22-27/3/2015. Invited talk: “Quantum Nuclei in Water by Path Integrals and Colored Noise”
\item NANOCEM Winter School, Århus, Denmark, 22-24/3/2015. Invited talk: “Metadynamics and longer time scales”
\item IPAM Workshop “Machine Learning for Many-Particle Systems”, IPAM/UCLA, Los Angeles 23-27/2/2015. Invited talk: “Finding patterns and drawing maps in the configuration space of materials and molecules”
\item CECAM/Psi-k Conference “Frontiers of first-principles simulations: materials design and discovery”, FHI Berlin, 1-5/2/2015. Invited talk: “Recognizing Patterns in Atomistic Simulations: Hydrogen Bonds, and Beyond”
}
\ifrecent{2014}{
\item CCMX Summer School “Atomic-scale Modelling of Materials”, EPFL, 1-3/9/2014. Keynote lecture: “Finite temperature: molecular dynamics”
\item VI Workshop in Electronvolt Neutron Spectroscopy: Frontiers and Horizons, The Cosener’s House (UK), 20-21/1/2014. Invited talk: “Inexpensive Evaluation of the Quantum Kinetic Energy and Particle Momentum Distribution by First-Principles Simulations”
}
\ifrecent{2013}{
\item TSRC Meeting “Quantum effects in condensed-phase systems”, Telluride (USA), 7-12/7/2013. Invited talk: “Nuclear quantum effects in first principles molecular dynamics by colored-noise thermostats”
\item CMCSN Coordination Meeting 2013, Davis (USA), 24-26/6/2013. Invited talk: “Nuclear quantum effects and hydrogen-bond fluctuations in water”
}
\ifrecent{2012}{
\item CECAM Workshop “Machine learning in atomistic simulations”, Lugano (Switzerland) 10-12/09/2012. Invited talk: “Understanding structural complexity with sketch map”
\item CMCSN Coordination Meeting 2012, Seattle (USA), 10-12/2/2012. Invited talk: “Nuclear quantum effects in ab initio MD: time to take off?”
}
\ifrecent{2011}{
\item CPMD Meeting 2011, Barcelona (Spain), 5-9/9/2011. Invited talk: “Enhancing molecular dynamics by colored-noise thermostats”
}
\ifrecent{2010}{
\item CMCSN Workshop “Structure and Dynamics of Water and Aqueous Solutions”, Princeton NJ (USA) 6-8/12/2010. Invited talk: “Coloring path integrals: an accelerated method to model nuclear quantum effects”, M. Ceriotti and M. Parrinello.
}
\ifrecent{2006}{
\item International School of Solid State Physics, 37th Course, Erice (Italy), 26-31/07/2006: Invited talk: “The fate of a $\mathrm{SiH}_{3}$ radical adsorbed on $\mathrm{Si}\left(100\right)$ surface: an ab-initio study”
}
\end{enumerate}

\section{Invited Seminars}
\begin{enumerate}
\ifrecent{2019}{
\item Sony Europe R\&D center, 10.04.2019, Stuttgart.
\item Physical and Theoretical Chemistry Laboratory, University of Oxford, 18.04.201. 
\item Department of Materials, Cambridge University, 24.04.2019. 
\item Department of Chemistry, Cambridge University, 24.04.2019. 
\item Thomas Young Center, Imperial College, 24.04.2019, London. 
}
\ifrecent{2018}{
\item Technische Universität Hamburg, 12.12.2018. (Inv. Prof. Meißner)
\item EPFL, Department of Physics, Theory Lunch Seminars, 20.11.2018. (Inv. Prof. Penedones)
\item EPFL, Sion Campus, 08.11.2018. (Inv. Prof. Queen and Agrawal)
\item University of Tokyo, Department of Materials Engineering, 31.08.2018. (Inv. Prof. Shibuta)
\item Karlsruhe Institute of Technology, Karlsruhe, 08.01.2018, Physical Chemistry Seminar Series (Prof. M. Elstner)
}
\ifrecent{2017}{
\item Theory Seminar Series CFEL-DESY, Hamburg, October 2017 (Prof. R. Santra)
\item Physics Colloquium, University of Luxembourg, May 2017 (Prof. A. Tkatchenko)
}
\ifrecent{2016}{
\item Empa Dübendorf, August 2016
\item TYC Soirée, University College London, July 2016
\item Institute of Computational Science, Universitá della Svizzera Italiana, Lugano, May 2016
\item Institute of Mathematics, EPFL Lausanne, February 2016
}
\ifrecent{2015}{
\item Institute of Science and Engineering, Kanazawa (Japan), November 2015
\item Institute for Condensed Matter, SISSA, Trieste, October 2015
\item Institut de Biologie Physico-Chimie / Ecole Normale Supérieure, Paris, June 2015
\item Department of Chemistry, University of Cambridge, June 2015
}
\ifrecent{2014}{
\item Department of Chemistry, University of Basel, November 2014
\item Thomas Young Centre, University College London, August 2014
\item Department of Materials Science, University of Milan - Bicocca, June 2014
\item Department of Materials Science, EPFL, February 2014
\item Department of Chemistry, University of Yale, February 2014 (Prof. Victor Batista)
\item Department of Chemistry, Ruhr University Bochum, January 2014 (Prof. Dominik Marx)
}
\ifrecent{2013}{
\item Department of Chemistry, Peking University, December 2013 (Prof. Jian Liu). 
\item Department of Physics, King's College London, March 2013
\item Department of Physics, University of Warwick, February 2013
\item Cavendish Laboratory, University of Cambridge, January 2013 (Prof. Bill Allison)
\item University of Chicago, Department of Chemistry, January 2013
}
\ifrecent{2012}{
\item Mini-Symposium “Computer Aided Chemistry”, ETH Zürich, November 2012
\item MPI Polymers, Mainz, November 2012 (Dr. Davide Donadio)
\item University College London, November 2012 (Prof. Angelos Michaelides)
\item MPI Biophysics, Frankfurt, October 2012 (Prof. Josè Faraldo-Gomez)
\item FHI-Berlin, September 2012 (Prof. Matthias Scheffler)
\item Physical and Theoretical Chemistry Lab., University of Oxford, April 2012
\item Department of Physics, University of California Berkeley, March 2012 (Prof. David Chandler)
\item Theoretical Chemistry Dept., Stanford University, March 2012 (Prof. Tom Markland)
\item Chemical Engineering Dept., University of Washington, February 2012 (Prof. Jim Pfaendtner)
}
\ifrecent{2011}{
\item Chemistry Dept, Columbia University, July 2011 (Prof. Bruce Berne)
\item Dept. of Materials Science, University of Oxford, March 2011 (Prof. Nicola Marzari)
}
\ifrecent{2010}{
\item Physical Chemistry and Physics Depts., October 2010 (Prof. Thomas Kühne)
\item Institute of Physical Chemistry, August 2010 (Prof. Jürg Hutter)
}
\ifrecent{2009}{
\item Department of Chemistry, University of Princeton, December 2009 (Prof. Roberto Car)
\item Department of Chemistry, University of Cambridge, November 2009 (Prof. Daan Frenkel)
\item Thomas Young Centre, Imperial College London, August 2009 (Prof. Mike Finnis)
}
\end{enumerate}
