\section{Teaching and Supervision}
\begin{itemize}
\item 3 PhD students successfully defended their thesis (Dr. Piero Gasparotto, Dr. Daniele Giofr\'e, Dr. Bingqing Cheng)
\item Currently supervising 9 PhD students (Edoardo Baldi, Venkat Kapil, Giulio Imbalzano, Andrea Anelli, Natalyia Lopanitsyna, Andrea Grisafi, Felix Musil, Benjamin Helfrecht, Chiheb Ben Mamhmoud)
\item Currently supervising 7 post-doctoral researchers (Dr. Michael Willatt, Dr. Federico Giberti, Dr. Edgar Engel, Dr. David Wilkins, Dr. Max Veit, Dr. Kevin Rossi, Dr. Albert Glensk), and have supervised in the past 7 post-doctoral researchers (Dr. Mariana Rossi, Dr. Riccardo Petraglia, Dr. Sandip De, Dr. Chungwen Liang, Dr. Gabriele Tocci, Prof. Robert Meißner, Dr. Rocio Semino).
\item MSc course on “Statistical Mechanics”, Institute of Materials, EPFL (4 ECTS credits, 51 hours)
\item BSc course on “Surfaces and Interfaces”, Institute of Materials, EPFL (3 ECTS credits, 39 hours)
\item 28 hours course for Master and Ph.D. students at EPFL “Statistical methods in atomistic computer simulations”
\item 8 hours lecture course on “Complex analysis and integral transforms” for the “MSc in Theoretical Chemistry” in Oxford, from January to March 2012, and from January to March 2013
\item Co-supervised two Master thesis students and two PhD Students at the University of Oxford
\end{itemize}

\section{Invited Lectures}
\begin{itemize}
\item TYC Masterclass, 13-14/7/2016, King's College London. Lecture Series on “Statistical Methods in Atomistic Modelling: Accelerated Sampling Through Machine-Learning”
\item 6 hours Ph.D. course on “Advanced sampling in atomistic simulations of complex systems”, PKU University, Beijing (Dec. 2013)
\end{itemize}
